### 2021-11-12 NSF2021/Description/specificaim3.tex
yny

We propose to investigate the effects of ion transport and distribution on the self-assembly of Janus particles within the HAP framework as follows.
First the Stokes equations in~\eqref{eq:stokes} are modified to incorporate the transport of ions as
\begin{equation}
\label{eq:EKstokes}
\begin{aligned}
  &-\Delta \mathbf{u} + \nabla p = \Delta\psi\cdot\nabla\psi, \qquad
  \nabla \cdot \mathbf{u} = 0,  \quad \mathbf{x} \in \Omega,\\
  &\delta^2\Delta\psi = -\frac{1}{2}\left(n_+-n_-\right),\qquad
  \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\qquad {\bf j}_{\pm} = -\nabla n_{\pm} \mp n_{\pm} \nabla\psi + \mbox{Pe} n_{\pm}\mathbf{u},
\end{aligned}
\end{equation}
where $\delta$ is the ratio of Debye screening length (inversely proportional to the square root of
ion concentration) to the particle size, 
$\mbox{Pe}$ is the Peclet number, a ratio between the convection and  thermal diffusion time scales.
$n_{+}$ ($n_{-}$) is the concentration of cation (anion).  In the limit of small $\delta$, PI Young and collaborator Y. Mori (U Penn) used asymptotic analyses to show that the jump in electric potential $\psi$ across the interface (zeta potential on the Janus particle surface) 
may give rise to different physical consequences such as electrophoresis \cite{Mori2018_JFM}.
%
An important question to address is: {\it How would such electrophoresis be affected by the HAP between two Janus particles?} 
As the first part of specific aim 3, we will address this important question. Results from this effort will help elucidate the effects of salt concentration on the assembly of Janus particles (\S~\ref{subsubsec:em_effects}).

We couple the electrokinetics in~\eqref{eq:EKstokes} with the mobility Janus particles in a viscous solvent through the velocity field, ion distribution, and the hydrophobic potential.  
First the screen length $\rho$ in the HAP model is now a function of the  cation concentrations: $\rho = \rho(n_+) =
\rho_0/\sqrt{1+c n_+}$ with a dimensionless parameter $c$. 
%
Secondly the value of the HAP may depend on the distribution of ions and electric potential right next to the particle surface \cite{Mori2018_JFM}.
Within this framework, we will first investigate the interaction between two Janus particles under HAP in an electrolytic solution described by the above
equations. We will conduct analytical calculations to investigate the effects of ion transport on the hydrophobic attraction between two Janus particles using the reciprocal theorem as in \cite{BayatiNajafi2016_JCP} for two Janus particles with a small surface activity.

\subsubsection{Electromechanical effects on the dynamic assembly of Janus particles \label{subsubsec:em_effects}}
Results from the proposed work in \S~\ref{subsubsec:JP_electrolyte} will shed light on how the electrokinetics described in~\eqref{eq:EKstokes}
may be simplified to a dielectric-like model where the bulk charges are constant, and the fluid flow and particle mobility are determined by the surface charge and the zeta potential as shown in \cite{Mori2018_JFM}. Under such simplification, the modified~\eqref{eq:EKstokes} may be re-formulated into integral forms. PI Young will conduct the asymptotic analyses to derive the modified~\eqref{eq:EKstokes}, and work with PI Quaife to design a numerical algorithm to simulate the modified system using integral formulation. We will first investigate the effects of salt concentration on the assembly of Janus particles to form helices, as shown in figure~\ref{fig:helices_of_JPs}.

>>>>

We propose to investigate the effects of ion transport and distribution on the self-assembly of Janus particles within the HAP framework as follows.
First the Stokes equations are modified to incorporate the transport of ions as
\begin{equation}
\label{eq:EKstokes}
\begin{aligned}
  &-\Delta \mathbf{u} + \nabla p = \Delta\psi\cdot\nabla\psi, \qquad
  \nabla \cdot \mathbf{u} = 0,  \quad \mathbf{x} \in \Omega,\\
  &\delta^2\Delta\psi = -\frac{1}{2}\left(n_+-n_-\right),\qquad
  \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\qquad {\bf j}_{\pm} = -\nabla n_{\pm} \mp n_{\pm} \nabla\psi + \mbox{Pe} n_{\pm}\mathbf{u},
\end{aligned}
\end{equation}
where $\delta$ is the ratio of Debye screening length (inversely proportional to the square root of
ion concentration) to the particle size, 
$\mbox{Pe}$ is the Peclet number, a ratio between the convection and  thermal diffusion time scales.
$n_{+}$ ($n_{-}$) is the concentration of cation (anion).  In the limit of small $\delta$, PI Young and collaborator Y. Mori (U Penn) used asymptotic analyses to show that the jump in electric potential $\psi$ across the interface (zeta potential on the Janus particle surface) 
may give rise to different physical consequences such as electrophoresis \cite{Mori2018_JFM}.
%
An important question to address is: {\it How would such electrophoresis be affected by the HAP between two Janus particles?} 
As the first part of specific aim 3, we will address this important question. Results from this effort will help elucidate the effects of salt concentration on the assembly of Janus particles (\S~\ref{subsubsec:em_effects}).

We couple the electrokinetics in~\eqref{eq:EKstokes} with the mobility  problem of Janus particles in a viscous solvent through the velocity field, ion distribution, and the hydrophobic potential.  
First the screen length $\rho$ in the HAP model is now a function of the  cation concentrations: $\rho = \rho(n_+) =
\rho_0/\sqrt{1+c n_+}$ with a dimensionless parameter $c$. 
%
Secondly the value of the HAP may depend on the distribution of ions and electric potential right next to the particle surface \cite{Mori2018_JFM}.
Within this framework, we will first investigate the interaction between two Janus particles under HAP in an electrolytic solution described by the above
equations. We will conduct analytical calculations to investigate the effects of ion transport on the hydrophobic attraction between two Janus particles using the reciprocal theorem as in \cite{BayatiNajafi2016_JCP} for two Janus particles with a small surface activity.

\subsubsection{Electromechanical effects on the dynamic assembly of Janus particles \label{subsubsec:em_effects}}
Results from the proposed work in \S~\ref{subsubsec:JP_electrolyte} will shed light on how the electrokinetics described in~\eqref{eq:EKstokes}
may be simplified to a dielectric-like model where the bulk charges are constant, and the fluid flow and particle mobility are determined by the surface charge and the zeta potential as shown in \cite{Mori2018_JFM}. Under such simplification, the modified~\eqref{eq:EKstokes} may be re-formulated into integral forms. PIs Ryham and Young will conduct the asymptotic analyses to derive the modified~\eqref{eq:EKstokes}, and work with PI Quaife to design a numerical algorithm to simulate the modified system using integral formulation. We will first investigate the effects of salt concentration on the assembly of Janus particles to form helices, as shown in figure~\ref{fig:helices_of_JPs}.
